\chapter{Tasks}
% List the tasks envisaged in solving the problem (May be sketchy at this
% point and will change during the course of the project).
The following is a list of the current and future tasks needed to competently deliver satisfactory results through the course of this project during semester one, and leading into semester two.
\section{Research - Preliminary and Ongoing}
Review of fundamental theory and concepts for understanding subject matter. This is involves reviewing fundamental engineering theory texts, academic texts and standards from engineering databases such as Institute of Electrical and Electronics Engineers (IEEE) online library.\\
Additionally, investigating existing ideas and proven research to confirm, or develop further intuition. This would involve content immediately relevant to the project aim, and use existing research to contrast the difference, and or benefits between ideas. By continuing ongoing comparisons of new and existing ideas, gives feasibly to develop or discontinue new ideas for the project.
\section{Modelling and Simulation}
Modelling is done with a mixture of written and computer based methods to gradually develop and build upon complex models. This requires heavy use of mathematical, and electrical and controls systems engineering theory.
\section{Model Optimisation}
Once a satisfactory model is developed, further methods will be applied to optimise system coefficients. This would primarily involve incorporating additional components such as parasitic disturbances, series resistance, or captured data of real world applications to develop a realistic model.
\section{Physical Proof of Concept I}
Building of a physical model, on confirmation that a satisfactory computer based model has been optimised in the best way possible. This would require extensive critiquing and final approval of the soft model before a physical development becomes a realisation.
\section{Further Developments}
Further developments are subject to project progression, suggestions, and new ideas.
