\chapter{Project Timeline}
% Project Time Line: An estimation of the times required for the various 
% tasks and a time line to complete these tasks (Gantt chart) and 
% explanation (if necessary). This should include work to be completed for
% BEB802 as well.
The working plan model of the project time-line has been broken up into four major phases for the period of semester one, leading into semester two. Of the four phases there is; firstly, initial research and basic modelling; secondly, model complexity development and optimisation; thirdly, adding realism and further optimisation; and finally, preparation for the first physical proof of concept model.
\input{proposal/flowchart/overview}
\newpage
\section{Phase One}
\input{proposal/flowchart/timeline1}
The first phase of the project has involved conducting research into academic articles, engineering texts, review of standards, and using websites to find examples of existing Matlab design algorithms and models. Furthermore, Matlab algorithms for LCL filter design were implemented tested, and revised.

\section{Phase Two}
\input{proposal/flowchart/timeline2}
Building on the LCL filter model, a state space model will be implemented using open loop system and adding a resonator. A closed loop model will then be created giving rise to the internal model principle and additional control law.

\section{Phase Three}
\input{proposal/flowchart/timeline3}
The control system model will be developed further, additional disturbances will be added to mimic certains aspects of a real system. This would include adding parasitic inductance and capacitance, switching dead-time, and small series resistances on capacitors and inductors.  

\section{Phase Four}
\input{proposal/flowchart/timeline4}
By this stage the inverter control system model is in it's final state. At this stage realisation of the physical model should be possible, avenues for converting the Matlab-Simulink control model onto a micro-controller should be possible. Additionally, due to the large gap between `Week 13' and `Semester Two', significant ground should be covered over this period, giving rise to a physical model by week one of semester two.